Progress with the NOSAMS<br>Hybrid Gas Ion Source

### 2021-05-03 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Fix image, minor edits.

---
title: "Progress with the NOSAMS<br>Hybrid Gas Ion Source"
author: "Brett Longworth"
institute: "NOSAMS/WHOI"
date: "2021/05/03"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

#### Flow control
* Change volume
* Add CO<sub>2</sub>
* Add helium

#### For a given sample size
* High inlet volume = low inlet pressure (NEC inlet)
* Low inlet volume = high inlet pressure (Ionplus inlet)

>>>>

---
title: "Progress with the NOSAMS<br>Hybrid Gas Ion Source"
author: "Brett Longworth, Josh Burton,<br>Josh Hlavenka, and Mark Roberts"
institute: "NOSAMS/WHOI"
date: "May 3, 2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

### Flow control
* Change volume
* Add CO<sub>2</sub>
* Add helium

### For a given sample size
* High inlet volume = low inlet pressure (NEC inlet)
* Low inlet volume = high inlet pressure (Ionplus inlet)
